### 2023-01-31 paper-thesis/chapters/31-comparing-with-lambdapi.tex
Fix the arrrows

\begin{figure}[ht]
	\begin{lstlisting}
rule TmType Type `↪` TmSort;
rule TmType (FnType $A $B) `↪` `Π` (x : TmType $A), TmType ($B x);
rule FnConstruct _ _ $f `↪` $f;
rule FnDestruct _ _ $f $a `↪` $f $a;
	\end{lstlisting}
	\caption{Reduction Rules for the Calculus of Constructions}
	\label{fig:lp-rules}
\end{figure}

@@

	\todo{invisible chars}
\begin{figure}[ht]
	\begin{lstlisting}
symbol Let : 
	`Π` (A : TmSort), 
	`Π` (B : TmType A → TmSort), 
	`Π` (v : TmType A),
	`Π` (b : TmType A → TmType (B v)),
	TmType (B v);
rule Let _ _ $v $b `↪` $b $v;
	\end{lstlisting}
	\caption{Definition of less powerful Let in lampdapi}
	\label{fig:lp-let}
\end{figure}

>>>>

\begin{figure}[ht]
	\begin{lstlisting}
rule TmType Type `$\hookrightarrow$` TmSort;
rule TmType (FnType $A $B) `$\hookrightarrow$` `Π` (x : TmType $A), TmType ($B x);
rule FnConstruct _ _ $f `$\hookrightarrow$` $f;
rule FnDestruct _ _ $f $a `$\hookrightarrow$` $f $a;
	\end{lstlisting}
	\caption{Reduction Rules for the Calculus of Constructions}
	\label{fig:lp-rules}
\end{figure}

@@

\begin{figure}[ht]
	\begin{lstlisting}
symbol Let : 
	`Π` (A : TmSort), 
	`Π` (B : TmType A → TmSort), 
	`Π` (v : TmType A),
	`Π` (b : TmType A → TmType (B v)),
	TmType (B v);
rule Let _ _ $v $b `$\hookrightarrow$` $b $v;
	\end{lstlisting}
	\caption{Definition of less powerful Let in lampdapi}
	\label{fig:lp-let}
\end{figure}
